POMDP comparisons across sigma_m, sigma_g

### 2018-01-30 appendix/appendix_recruit_first.Rmd
fix log dir

options(mc.cores=parallel::detectCores())
```

@@

```{r}
meta <- expand.grid(sigma_g = c(0.02, 0.1, 0.15), 
                    sigma_m = c(0, 0.1, 0.15),
                    stringsAsFactors = FALSE) %>%
        mutate(scenario  = as.character(1:length(sigma_m)))
log_dir <- "appendix_alphas" # Store the computed solution files here
meta
```

@@

```{r}
options(mc.cores=1)
```

>>>>

options(mc.cores=parallel::detectCores())
log_dir <- "../data/observe_recruit_harvest" # Store the computed solution files here

@@

```{r}
meta <- expand.grid(sigma_g = c(0.02, 0.1, 0.15), 
                    sigma_m = c(0, 0.1, 0.15),
                    stringsAsFactors = FALSE) %>%
        mutate(scenario  = as.character(1:length(sigma_m)))
meta
```

@@
